Interactively Visualizing Multivariate Market Segmentation Using pytourr

### 2024-09-26 manuscript.tex
References added

A first step may look into what variables are important for the cluster solution. The interface provides different capabilites that support variable selection. First, a 2D tour view can be used to understand the sensitivity of the grouping to individual varaibles, in particular when using the manual tour to remove one variable at a time. This is in particular useful when the starting view was obtained through a projection pursuit guided tour REF that optimized for the separation between the labeled groups REF.

>>>>

A first step may look into what variables are important for the cluster solution. The interface provides different capabilites that support variable selection. First, a 2D tour view can be used to understand the sensitivity of the grouping to individual varaibles, in particular when using the manual tour to remove one variable at a time. This is in particular useful when the starting view was obtained through a projection pursuit guided tour~\cite{CBCH94} that optimized for the separation between the labeled groups~\cite{lckl2005}.
